Turbulence and Particle Acceleration in Giant Radio Halos: the Origin of Seed Electrons

### 2016-05-13 paper.tex
edits

The alternative model for RHs is re-energization of seed suprathermal
electrons by Fermi II acceleration when ICM turbulence becomes
transonic during mergers
\citep{1987A&A...182...21S,1993ApJ...406..399G,2001MNRAS.320..365B,
  2004MNRAS.350.1174B,brunetti07,brunetti11,2015ApJ...800...60M}. Due
to the short radiative cooling time of high-energy relativistic
electrons, the cluster synchrotron emission quickly fades away after a
merger, which naturally explains the observed bimodality of RHs
\cite[see e.g.][]{2013MNRAS.429.3564D,2014MNRAS.443.3564D}.

@@

However, we assume a simplified and stationary model for magnetic
fields and turbulence. We do not account for the time-varying energy
density in compressible waves, which are thought to be necessary for
the acceleration process \citep{brunetti07,brunetti11}, as the cluster
merger proceeds.  So our approach is orthogonal (and complementary) to
e.g., simulations of \citealp{2015ApJ...800...60M} that focus on the
time-dependent compressible turbulence while adopting a simplified
treatment of CR that does not follow the transport of the CR
distribution function. Our approach of parametrizing turbulence
enables us to vary parameters associated with the unknown continuation
of magneto-hydrodynamical (MHD) turbulence below the MHD scale and the
overall amplitude of compressible waves (that can in principle vary
depending on the details of a particular cluster merger).

@@

To pursue these three possibilities further, we employ cosmological
simulations of CRs in clusters. In tandem with new insights from our
recent work on DSA generated fossil electrons \citep{pinzke13}, we
generate the first quantitative calculation of primary and secondary
seed electrons and compare to observations in the Coma cluster. For
the most part, we adopt parameters that are used in previous work,
including Fermi-II acceleration with models of turbulent spectra
\citep{brunetti07,brunetti11}, injection scale of turbulence
\citep{2015ApJ...800...60M}, the energy density of turbulence
\citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V},
for CR acceleration in shocks \citep[][in particular $K_{\rmn{ep}}$
  and the acceleration efficiency]{pinzke13}, and for cosmological
simulations with CR physics \citep[][i.e., shock history,
  temperature profile, density profile, magnetic field
  profile]{pinzke10}. All these parameters are uncertain, and could
potentially change our predictions. We refer the reader to
section~\ref{sect:param_comp} for a first exploration of parameter
space, however we leave the detailed exploration of parameter space and
the interaction between free parameters to future work.

@@

During post-processing of our Coma-like cluster simulation, we solve
the Fokker-Planck equation over a redshift interval from $z=5$ to
0. The simulated cluster undergoes a major merger over the last
1-2~Gyrs that is thought to inject large turbulent eddies. Following
standard approaches
\citep{brunetti07,brunetti11,2004ApJ...614..757Y,2015ApJ...800...60M}
we assume that about one Gyr after core passage the fields have
decayed down to the smallest scales where reacceleration is most
efficient ($D_{pp}\sim k_\rmn{cut}$) and the radio halo turns on
shortly after. Note that the exact decay time of the turbulens is of
minor importance, since the thermal and CR quantities are very similar
a few 100 Myrs before and after $z=0$ where we have chosen to evaluate
the simulations. This delay naturally explains why giant radio halos
are only seen in a fraction of all merging clusters.

@@

All of the physics of turbulent reacceleration is effectively encapsulated in the diffusion coefficient, which can be rewritten as \citep{2015ApJ...800...60M}:
\begin{equation}
D_{pp}(p) = \frac{ p^{2} \pi I_{\theta}(c_{s}/c)}{8 c} \langle k \rangle_{\mathcal{W}} \langle (\delta v_{\rm c})^{2} \rangle
\label{eqn:diffusion}
\end{equation}
\SPO{define $I_{\theta}(c_{s}/c)$ or explain its meaning in words and point to the definition provided in the next subsection.}
where
\begin{equation}
\langle k \rangle_{\mathcal{W}} = \frac{1}{\langle (\delta \varv_{\rm c})^{2} \rangle} \int_{k_{\rm L}}^{k_{\rm cut}} dk \, k \, \mathcal{W}(k) \approx \frac{s-1}{2-s} k_{\rm L} \left( \frac{k_{\rm cut}}{k_{\rm L}} \right)^{2-s} 
\end{equation}
is an energy-averaged wavenumber, $k_{\rm L}, k_{\rm cut}$ are the wavenumbers associated with the outer scale and the cutoff scale respectively, and we have assumed a total energy spectrum (both kinetic and potential energy, where the two are assumed to be in equipartition \citep{sarkar11}): 
\begin{equation}
\mathcal{W}(k) = \frac{(s-1) \langle (\delta \varv_{\rm c})^{2} \rangle}{k_{\rm L}} \left( \frac{k}{k_{\rm L}} \right)^{-s} 
\label{eqn:Wk}
\end{equation}
which defines the normalization $\langle (\delta \varv_{\rm c})^{2} \rangle$ (the subscript 'c' emphasizes that we specialize to compressive modes). Intuitively, we can understand the form of the the diffusion coefficient from the fact that for second-order Fermi acceleration, $\dot{p} \sim \Delta p/\tau \sim p\,\langle k c \rangle_{\mathcal{W}} (\delta \varv_{\rm c}/c)^{2}$, where $\tau^{-1} \sim \langle k c \rangle_{\mathcal{W}}$ is the energy averaged wave-particle interaction rate, and $\Delta p \sim p (\delta \varv_{\rm c}/c)^{2}$ is the typical momentum change during wave particle scattering. Thus: 
\begin{equation}
D_{pp} \sim p \dot{p} \sim p^{2} \langle k c \rangle_{\mathcal{W}} \left( \frac{\delta \varv_{\rm c}}{c} \right)^{2}. 
\end{equation}

@@

{\bf Energy in compressive modes} The total turbulence energy is typically $\sim 15-70\%$ of the thermal energy in a cluster \citep{vazza11}; it rises rapidly during a merger. The compressible component is $\sim 20-40\%$ of the total turbulent energy, and shows more rapid temporal variations compared to the compressible component \citep{2013ApJ...771..131B,2015ApJ...800...60M}. It is worth noting that in the subsonic regime of the solar wind \citep{yao11,howes12}, as well as most idealized calculations of turbulent driving, there is relatively little energy in the fast mode. For instance, the fiducial simulations of \citet{lynn14} with a sonic Mach number ${\mathcal M}_{\rm s} \sim 0.35$ and a plasma beta factor of $\beta \sim 1$ show that 50\%, 45\%, 5\% of the turbulent energy density is in the Alfv{\'e}n, slow, and fast modes, respectively. For higher $\beta \sim 3-10$, they find that the proportion of energy in fast modes drops to $< 1\%$, while the fraction of energy in the slow mode remains roughly the same. Similarly, \citet{kowal10} find that the fast mode is highly subdominant (see their Table 2); for the run most relevant to cluster conditions ${\mathcal M}_{\rm s} \sim 0.7, \beta \sim 10$, they find $\sim 42\%, 6\%$ of turbulent energy in slow and fast modes respectively. These simulations are roughly consistent with theoretical estimates of $U_{\rm fast}/U_{\rm slow} \sim {\mathcal M}_{\rm s}^{2}/{\mathcal M}_{\rm A}$ \citep{cho03}. By contrast, MHD simulations of galaxy clusters find a large fraction ($\sim 25$\%) of turbulent energy in fast modes \citep{2013ApJ...771..131B}. This is likely due to the compressive nature of turbulent driving (transonic infall and merger), whereas idealized simulations tend to use incompressible solenoidal driving and allow compressive fluctuations to develop on their own.

In the high-$\beta$, subsonic conditions of the ICM, the Alfv{\'e}n/slow modes are exactly/approximately incompressible, and so the approximate identification of compressive modes with fast modes is valid. We therefore take $\sim 25\%$ of the turbulent energy density in compressive fast modes as a reasonable baseline estimate \citep{2013ApJ...771..131B,2015ApJ...800...60M}. If a large fraction of energy is in slow modes, then resonant broadening of wave-particle interactions can render slow modes an efficient acceleration mechanism \citep{lynn14}, as we discuss briefly in \S\ref{?}.

@@

Finally, if turbulence is transonic ($M_{\rm s} \sim {\mathcal O}(1)$), then compressible modes can dissipate in weak shocks, as seen in decompositions of the velocity field into solenoidal/compressible components both in idealized simulations \citep{kowal10,porter15}, and cosmological hydrodynamic simulations \citep{2015ApJ...800...60M}. The compressible component has a steep Burgers ($s=2$) spectrum. Burgers turbulence is distinct from other forms of turbulence in that it violates locality in k-space--i.e., power does not gradually cascade, but instead can directly jump from large to small scales via a network of weak shocks. Since the Fourier transform of a step function goes as $k^{-1}$, Burgers turbulence has a power spectrum of $P(k) \propto k^{-2}$. If we contrast the different velocity scalings: $\varv \propto l^{1/4}$ (Kraichnan), $\varv \propto l^{1/3}$ (Kolmogorov), $\varv \propto l^{1/2}$ (Burgers), we see that because of its dissipative nature, Burgers turbulence is the least efficient at transferring energy towards the small scales needed (since the wave particle interaction rate scales as $k$) for efficient acceleration. If Burgers turbulence dominates, then particle acceleration rates are too slow in the face of cooling processes to explain radio halos \citep{2015ApJ...800...60M}.

@@

The profile of injected turbulence depends on the details of the
merger such as time during the merger, the impact parameter, the
merger mass ratio, and the degree of cluster anisotropy
\citep{2015ApJ...800...60M}. We parametrize these uncertainties and
assume that it scales with the thermal energy density to some
power. Hence we assume volumetric injection rate of turbulent energy,
$I_0\propto \eps_\rmn{th}^{\alpha_\rmn{tu}}$, and determine the
normalization by requiring that the turbulent energy in compressible
modes $E_\rmn{turb}=\int \int \mathcal{W}(k) \rmn{d}k \rmn{d}V =
X_\rmn{tu} E_\rmn{th}$, where $E_\rmn{th}$ is the total thermal
energy. We adopt a turbulent energy ratio $X_\rmn{tu}=0.2$ within the
radio halo.\footnote{Simulations show that the compressible modes
  contribute a factor $0.2-0.4$ to the total turbulent energy
  \citep{2013ApJ...771..131B,2015ApJ...800...60M}. Furthermore, the
  total turbulent energy, which can be decomposed into a slenoidal and
  compressible component, is typically $\sim15-70$\% of the thermal
  energy in a cluster \citep{2011A&A...529A..17V}; in agreement with
  our adopted value of $X_\rmn{tu}$.}

@@

% --- section: Analytical Results and discussion --- %
\section{Parameter space exploration with spherical models}
\label{sect:param_comp}
In this paper we rely on several critical parameters describing
relatively unknown non-thermal physics in the ICM. Here we develop a
simplified framework that will be used to explore how radio emission
depends on these parameters. Our fiducial model is meant to be
compared against the Coma cluster.

@@

In order to quickly explore this parameter space, we solve the
Fokker-Planck equation in static spherical shells for injection,
reacceleration, and losses of the CRs, i.e., we neglect Lagrangian
evolution during re-acceleration.  This ignores the effect of
adiabatic compressive heating of the CRs, though this is generally
subdominant (e.g., see Fig. 7 of \citealt{2015ApJ...800...60M}). Once
the CRs have been reaccelerated for $\tau_\rmn{cl} = 650\,\rmn{Myr}$,
we calculate the resulting radio emission numerically using the
formalism outlined in \cite{1979rpa..book.....R} and compare the
emission profiles and spectra as we vary one parameter at a time
relative to our fiducial model.

We adopt both the density \citep{1992A&A...259L..31B} and temperature
profiles \citep{2009ApJ...696.1886B,2001A&A...365L..67A} derived from
X-ray observations of the Coma cluster,
\begin{eqnarray}
n_e &=& n_0\,\left[1+\left(R/R_{\rmn{c}}\right)^2\right]^{-1.125},\nonumber\\
k_{\rmn{B}} T &=& 8.25\,\rmn{keV} \left[1+\left(2R/R_{200}\right)^2\right]^{-0.32},
\end{eqnarray}
with $n_0=3.4\times10^{-3}\,\rmn{cm}^{-3}$.  The virial and core radii
of Coma are given by $R_{200} = 2.3\,\rmn{Mpc}$
\citep{2002ApJ...567..716R} and $R_{\rmn{c}} = 294\,\rmn{kpc}$,
respectively. In accordance with rotation measure measurements, we assume $B(r)=B_{0} (n/n_{0})^{\eta}$, where $B_{0}=4.8 \mu$G and $\eta=0.5$ \citep{bonafede10}.

@@

Larger levels of turbulence also {\it increase} spectral curvature, which might seem puzzling. It can be understood as follows. The pre-acceleration electron distribution function can be understood as a result of competition between injection $f \propto p^{-\alpha_{\rm inj}}$ and cooling. At low momenta, when the Coulomb cooling time is short, $f \propto p^{-\alpha_{\rm inj}+1}$, at high momenta, when inverse Compton/synchrotron cooling dominates, $f \propto p^{-\alpha_{\rm inj} -1}$. In between, there is a quasi-adiabatic regime where electrons accumulate (for more details, and an analytic self-similar solution, see \citealt{1999ApJ...520..529S, pinzke13}). In the absence of cooling, momentum advection in the limit $D_{pp} \propto p^{2}$ (so that $\tau =p^{2}/4 D_{pp}$ is momentum independent) simply shifts the distribution $f(p) \rightarrow f(A p)$. 
When the acceleration efficiency is low, most observable emission corresponds to the power-law tail of the distribution function $f \propto p^{-\alpha_{\rm inj}-1}$ set by the balance between injection and synchrotron/IC cooling. However, as the acceleration efficiency $A$ increases, radio emission starts to probe the 'bump' around $p_{*}$ (given by $\tau_{\rm D} \sim \tau_{\rm cool}(p_{*})$) where electrons accumulate and the distribution function is curved. This results in a curved emission spectrum. The synchrotron spectrum steepens at the frequency \citep{brunetti01}: 
\begin{equation}
\nu_{\rm s} \propto \frac{B \tau_{\rm D}^{-2}}{(B^{2}+B^{2}_{\rm CMB})^{2}}
\end{equation}
where $B_{\rm CMB} \equiv (8 \pi U_{\rm CMB})^{1/2}$, which increases for shorter $\tau_{\rm D}$.

{\bf Impact of spatial profile of turbulence ($\alpha_{\rm tu}$)} From the middle panels of Fig.~\ref{fig:param_comp}, we see that as expected, a flatter turbulence profile directly translates into a flatter radio surface brightness profile. Since seed electrons are more concentrated toward the center (the collisional production of secondaries is more rapid there), and B-fields are higher, concentrating the turbulence toward the cluster center for fixed $X_{\rm tu}$ results in higher radio luminosities, and slightly more curvature (due to the increased importance of cooling near the center). Overall, however, the spatial profile of turbulence has a much weaker effect than its overall normalization.

{\bf Impact of spatial profile of seed CRs $\alpha_{\rm CR, spat}$} The spatial distribution of CRs has an even smaller impact on radio emission. At fixed total CR energy content $X_{\rm CR}$, concentrating the CRs towards the center leads to more centrally dominated surface brightness profiles, as expected, and higher radio luminosities (for the same reasons as above: secondaries are more easily produced in the center, and B-fields are higher). We have also confirmed that radio surface brightness profiles scale linearly with $X_{\rm CR}$, as expected.

Overall, our results suggest that radio halos are much more sensitive to the level of turbulence (exponential dependence) rather than CR abundance (linear dependence), and that the spatial distribution of turbulence and CRs, while important, are second-order effects. In our parametrization, the most important controlling variable is $X_{\rm tu}$. The overall level of turbulence has to be such that $\tau_{\rm D} \sim \tau_{\rm cl}$ (see Table \ref{tab:timescales}), otherwise, too little or too much amplification takes place. For instance, for
$X_\rmn{tu}\gtrsim0.08$, changing $X_\rmn{tu}$ by a factor of two
changes the radio surface brightness by a factor of $\sim 10-100$ (see top panels of Fig.~\ref{fig:param_comp}). The required $\tau_{\rm D}/\tau_{\rm cl}$ depends only logarithmically on the abundance of seed CRs. While the requirement of a threshold level of turbulence may explain why radio brightness is bimodal, it also raises a fine-tuning problem: why is the $L_{\rm radio}$ vs. $L_{\rm X}$ relation in active radio halos so tight? Depending on the details of infall or mergers, we would naturally expect fluctuations in $X_{\rm tu}$, which would translate into large scatter in the $L_{\rm radio}--L_{\rm X}$ relation. This can only make sense if the timescale over which acceleration takes place $\tau_{\rm cl}$ also depends on the properties of turbulence, so that the the ratio $\tau_{\rm D}/\tau_{\rm cl}$ has relatively little scatter. We discuss one such scenario in \S\ref{sec:reacc}, but this point clearly deserves more work.

@@

The standard reacceleration model for radio halos requires two ingredients with no current direct observational constraints: a CR population which produces seed electrons, and turbulence to perform Fermi II acceleration on these electrons\footnote{Other model ingredients, such as temperature, density, and B-field profiles, are observationally constrained by X-ray and Faraday rotation measurements.}. For the best studied radio halo, Coma, there are two main observational constraints: the radio surface brightness profile $S_{\rm nu}(r)$, and the integrated luminosity as a function of frequency $L(\nu)$. For certain assumptions about turbulence and the seed population, analytic theoretical models can match these observations \citep{brunetti11}, but the realism of the assumed seed electron and turbulent profiles must be confronted with numerical simulations. Cluster turbulence has been studied numerically in cosmological simulations with an eye toward radio halo properties \citep{donnert13,beresnyak13,miniati15}, though they were not confronted against the two benchmark observations mentioned above. {\bf Is the latter statement too provocative, remove?} More glaringly, direct simulation of the seed electron population has been woefully missing in the literature. In this paper, we fill that gap. At the same time, we study the sensitivity of radio halo profiles and spectra to variation in properties of turbulence and seed population, and uncover the dominant effects.

>>>>

The alternative model for RHs is re-energization of seed suprathermal
electrons by Fermi II acceleration when ICM turbulence becomes
transonic during mergers
\citep{1987A&A...182...21S,1993ApJ...406..399G,2001MNRAS.320..365B,
  2004MNRAS.350.1174B,brunetti07,brunetti11,miniati15}. Due
to the short radiative cooling time of high-energy relativistic
electrons, the cluster synchrotron emission quickly fades away after a
merger, which naturally explains the observed bimodality of RHs
\cite[see e.g.][]{2013MNRAS.429.3564D,2014MNRAS.443.3564D}.

@@

However, we assume a simplified and stationary model for magnetic
fields and turbulence. We do not account for the time-varying energy
density in compressible waves, which are thought to be necessary for
the acceleration process \citep{brunetti07,brunetti11}, as the cluster
merger proceeds.  So our approach is orthogonal (and complementary) to
e.g., simulations of \citealp{miniati15} that focus on the
time-dependent compressible turbulence while adopting a simplified
treatment of CR that does not follow the transport of the CR
distribution function. Our approach of parametrizing turbulence
enables us to vary parameters associated with the unknown continuation
of magneto-hydrodynamical (MHD) turbulence below the MHD scale and the
overall amplitude of compressible waves (that can in principle vary
depending on the details of a particular cluster merger).

@@

To pursue these three possibilities further, we employ cosmological
simulations of CRs in clusters. In tandem with new insights from our
recent work on DSA generated fossil electrons \citep{pinzke13}, we
generate the first quantitative calculation of primary and secondary
seed electrons and compare to observations in the Coma cluster. For
the most part, we adopt parameters that are used in previous work,
including Fermi-II acceleration with models of turbulent spectra
\citep{brunetti07,brunetti11}, injection scale of turbulence
\citep{miniati15}, the energy density of turbulence
\citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V},
for CR acceleration in shocks \citep[][in particular $K_{\rmn{ep}}$
  and the acceleration efficiency]{pinzke13}, and for cosmological
simulations with CR physics \citep[][i.e., shock history,
  temperature profile, density profile, magnetic field
  profile]{pinzke10}. All these parameters are uncertain, and could
potentially change our predictions. We refer the reader to
section~\ref{sect:param_comp} for a first exploration of parameter
space, however we leave the detailed exploration of parameter space and
the interaction between free parameters to future work.

@@

During post-processing of our Coma-like cluster simulation, we solve
the Fokker-Planck equation over a redshift interval from $z=5$ to
0. The simulated cluster undergoes a major merger over the last
1-2~Gyrs that is thought to inject large turbulent eddies. Following
standard approaches
\citep{brunetti07,brunetti11,2004ApJ...614..757Y,miniati15}
we assume that about one Gyr after core passage the fields have
decayed down to the smallest scales where reacceleration is most
efficient ($D_{pp}\sim k_\rmn{cut}$) and the radio halo turns on
shortly after. Note that the exact decay time of the turbulens is of
minor importance, since the thermal and CR quantities are very similar
a few 100 Myrs before and after $z=0$ where we have chosen to evaluate
the simulations. This delay naturally explains why giant radio halos
are only seen in a fraction of all merging clusters.

@@

All of the physics of turbulent reacceleration is effectively encapsulated in the diffusion coefficient, which can be rewritten as \citep{miniati15}:
\begin{equation}
D_{pp}(p) = \frac{ p^{2} \pi I_{\theta}(c_{s}/c)}{8 c} \langle k \rangle_{\mathcal{W}} \langle (\delta v_{\rm c})^{2} \rangle
\label{eqn:diffusion}
\end{equation}
\SPO{define $I_{\theta}(c_{s}/c)$ or explain its meaning in words and point to the definition provided in the next subsection.}
where
\begin{equation}
\langle k \rangle_{\mathcal{W}} = \frac{1}{\langle (\delta \varv_{\rm c})^{2} \rangle} \int_{k_{\rm L}}^{k_{\rm cut}} dk \, k \, \mathcal{W}(k) \approx \frac{s-1}{2-s} k_{\rm L} \left( \frac{k_{\rm cut}}{k_{\rm L}} \right)^{2-s} 
\end{equation}
is an energy-averaged wavenumber, $k_{\rm L}, k_{\rm cut}$ are the wavenumbers associated with the outer scale and the cutoff scale respectively, and we have assumed a total energy spectrum (both kinetic and potential energy, where the two are assumed to be in equipartition \citep{sarkar11}): 
\begin{equation}
\mathcal{W}(k) = \frac{(s-1) \langle (\delta \varv_{\rm c})^{2} \rangle}{k_{\rm L}} \left( \frac{k}{k_{\rm L}} \right)^{-s} 
\label{eqn:Wk}
\end{equation}
which defines the normalization $\langle (\delta \varv_{\rm c})^{2} \rangle$ (the subscript 'c' emphasizes that we specialize to compressive modes). Intuitively, we can understand the form of the the diffusion coefficient from the fact that for second-order Fermi acceleration, $\dot{p} \sim \Delta p/\tau \sim p\,\langle k c \rangle_{\mathcal{W}} (\delta \varv_{\rm c}/c)^{2}$, where $\tau^{-1} \sim \langle k c \rangle_{\mathcal{W}}$ is the energy averaged wave-particle interaction rate, and $\Delta p \sim p (\delta \varv_{\rm c}/c)^{2}$ is the typical momentum change during wave particle scattering. Thus: 
\begin{equation}
D_{pp} \sim p \dot{p} \sim p^{2} \langle k c \rangle_{\mathcal{W}} \left( \frac{\delta \varv_{\rm c}}{c} \right)^{2}. 
\end{equation}

@@

{\bf Energy in compressive modes} The total turbulence energy is typically $\sim 15-70\%$ of the thermal energy in a cluster \citep{vazza11}; it rises rapidly during a merger. The compressible component is $\sim 20-40\%$ of the total turbulent energy, and shows more rapid temporal variations compared to the compressible component \citep{2013ApJ...771..131B,miniati15}. It is worth noting that in the subsonic regime of the solar wind \citep{yao11,howes12}, as well as most idealized calculations of turbulent driving, there is relatively little energy in the fast mode. For instance, the fiducial simulations of \citet{lynn14} with a sonic Mach number ${\mathcal M}_{\rm s} \sim 0.35$ and a plasma beta factor of $\beta \sim 1$ show that 50\%, 45\%, 5\% of the turbulent energy density is in the Alfv{\'e}n, slow, and fast modes, respectively. For higher $\beta \sim 3-10$, they find that the proportion of energy in fast modes drops to $< 1\%$, while the fraction of energy in the slow mode remains roughly the same. Similarly, \citet{kowal10} find that the fast mode is highly subdominant (see their Table 2); for the run most relevant to cluster conditions ${\mathcal M}_{\rm s} \sim 0.7, \beta \sim 10$, they find $\sim 42\%, 6\%$ of turbulent energy in slow and fast modes respectively. These simulations are roughly consistent with theoretical estimates of $U_{\rm fast}/U_{\rm slow} \sim {\mathcal M}_{\rm s}^{2}/{\mathcal M}_{\rm A}$ \citep{cho03}. By contrast, MHD simulations of galaxy clusters find a large fraction ($\sim 25$\%) of turbulent energy in fast modes \citep{2013ApJ...771..131B}. This is likely due to the compressive nature of turbulent driving (transonic infall and merger), whereas idealized simulations tend to use incompressible solenoidal driving and allow compressive fluctuations to develop on their own.

In the high-$\beta$, subsonic conditions of the ICM, the Alfv{\'e}n/slow modes are exactly/approximately incompressible, and so the approximate identification of compressive modes with fast modes is valid. We therefore take $\sim 25\%$ of the turbulent energy density in compressive fast modes as a reasonable baseline estimate \citep{2013ApJ...771..131B,miniati15}. If a large fraction of energy is in slow modes, then resonant broadening of wave-particle interactions can render slow modes an efficient acceleration mechanism \citep{lynn14}, as we discuss briefly in \S\ref{?}.

@@

Finally, if turbulence is transonic ($M_{\rm s} \sim {\mathcal O}(1)$), then compressible modes can dissipate in weak shocks, as seen in decompositions of the velocity field into solenoidal/compressible components both in idealized simulations \citep{kowal10,porter15}, and cosmological hydrodynamic simulations \citep{miniati15}. The compressible component has a steep Burgers ($s=2$) spectrum. Burgers turbulence is distinct from other forms of turbulence in that it violates locality in k-space--i.e., power does not gradually cascade, but instead can directly jump from large to small scales via a network of weak shocks. Since the Fourier transform of a step function goes as $k^{-1}$, Burgers turbulence has a power spectrum of $P(k) \propto k^{-2}$. If we contrast the different velocity scalings: $\varv \propto l^{1/4}$ (Kraichnan), $\varv \propto l^{1/3}$ (Kolmogorov), $\varv \propto l^{1/2}$ (Burgers), we see that because of its dissipative nature, Burgers turbulence is the least efficient at transferring energy towards the small scales needed (since the wave particle interaction rate scales as $k$) for efficient acceleration. If Burgers turbulence dominates, then particle acceleration rates are too slow in the face of cooling processes to explain radio halos \citep{miniati15}.

@@

The profile of injected turbulence depends on the details of the
merger such as time during the merger, the impact parameter, the
merger mass ratio, and the degree of cluster anisotropy
\citep{miniati15}. We parametrize these uncertainties and
assume that it scales with the thermal energy density to some
power. Hence we assume volumetric injection rate of turbulent energy,
$I_0\propto \eps_\rmn{th}^{\alpha_\rmn{tu}}$, and determine the
normalization by requiring that the turbulent energy in compressible
modes $E_\rmn{turb}=\int \int \mathcal{W}(k) \rmn{d}k \rmn{d}V =
X_\rmn{tu} E_\rmn{th}$, where $E_\rmn{th}$ is the total thermal
energy. We adopt a turbulent energy ratio $X_\rmn{tu}=0.2$ within the
radio halo.\footnote{Simulations show that the compressible modes
  contribute a factor $0.2-0.4$ to the total turbulent energy
  \citep{2013ApJ...771..131B,miniati15}. Furthermore, the
  total turbulent energy, which can be decomposed into a slenoidal and
  compressible component, is typically $\sim15-70$\% of the thermal
  energy in a cluster \citep{2011A&A...529A..17V}; in agreement with
  our adopted value of $X_\rmn{tu}$.}

@@

% --- section: Analytical Results and discussion --- %
\section{Parameter space exploration with spherical models}
\label{sect:param_comp}
In this paper we rely on several critical parameters describing
relatively unknown non-thermal physics in the ICM. Here we develop a
simplified framework for our reacceleration model of secondary
electrons. We will explore how radio emission depends on the
parameters describing the spatial profile of CR protons and
turbulence, thereby semi-analytically probing variations about the
models \Mflatturb and \Mstream. Our fiducial model is meant to be
compared against the Coma cluster.

@@

In order to quickly explore this parameter space, we solve the
Fokker-Planck equation in static spherical shells for injection,
reacceleration, and losses of the CRs, i.e., we neglect Lagrangian
evolution during re-acceleration.  This ignores the effect of
adiabatic compressive heating of the CRs, though this is generally
subdominant (e.g., see Fig. 7 of \citealt{miniati15}). Once
the CRs have been reaccelerated for $\tau_\rmn{cl} = 650\,\rmn{Myr}$,
we calculate the resulting radio emission numerically using the
formalism outlined in \cite{1979rpa..book.....R} and compare the
emission profiles and spectra as we vary one parameter at a time
relative to our fiducial model.

We adopt both the density \citep{1992A&A...259L..31B} and temperature
profiles \citep{2009ApJ...696.1886B,2001A&A...365L..67A} derived from
X-ray observations of the Coma cluster,
\begin{eqnarray}
n_e &=& n_0\,\left[1+\left(R/R_{\rmn{c}}\right)^2\right]^{-1.125},\nonumber\\
k_{\rmn{B}} T &=& 8.25\,\rmn{keV} \left[1+\left(2R/R_{200}\right)^2\right]^{-0.32},
\end{eqnarray}
with $n_0=3.4\times10^{-3}\,\rmn{cm}^{-3}$.  The virial and core radii
of Coma are given by $R_{200} = 2.3\,\rmn{Mpc}$
\citep{2002ApJ...567..716R} and $R_{\rmn{c}} = 294\,\rmn{kpc}$,
respectively. In accordance with Faraday rotation measure
measurements, we assume $B(r)=B_{0} (n/n_{0})^{\eta}$, where
$B_{0}=4.8 \mu$G and $\eta=0.5$ \citep{bonafede10}.

@@

Larger levels of turbulence also {\it increase} spectral curvature, which might seem puzzling. It can be understood as follows. The pre-acceleration electron distribution function can be understood as a result of competition between hadronic injection $f \propto p^{-\alpha_{\rm inj}}$ and cooling, which results in a quasi-steady state for the non-thermal (secondary) electrons. At low momenta, when the Coulomb cooling time is short, $f \propto p^{-\alpha_{\rm inj}+1}$, at high momenta, when inverse Compton/synchrotron cooling dominates, $f \propto p^{-\alpha_{\rm inj} -1}$. In between, there is a quasi-adiabatic regime where electrons accumulate (for more details, and an analytic self-similar solution, see \citealt{1999ApJ...520..529S, pinzke13}). In the absence of cooling, momentum advection in the limit $D_{pp} \propto p^{2}$ (so that $\tau =p^{2}/4 D_{pp}$ is momentum independent) simply shifts the distribution $f(p) \rightarrow f(A p)$. 
When the acceleration efficiency is low, most observable emission corresponds to the power-law tail of the distribution function $f \propto p^{-\alpha_{\rm inj}-1}$ set by the balance between injection and synchrotron/IC cooling. However, as the acceleration efficiency $A$ increases, radio emission starts to probe the 'bump' around $p_{*}$ (given by $\tau_{\rm D} \sim \tau_{\rm cool}(p_{*})$) where electrons accumulate and the distribution function is curved. This results in a curved emission spectrum. The synchrotron spectrum steepens at the frequency \citep{2001MNRAS.320..365B}: 
\begin{equation}
\nu_{\rm s} \propto \frac{B \tau_{\rm D}^{-2}}{(B^{2}+B^{2}_{\rm CMB})^{2}}
\end{equation}
where $B_{\rm CMB} \equiv (8 \pi U_{\rm CMB})^{1/2}$, which increases for shorter $\tau_{\rm D}$.

{\bf Impact of spatial profile of turbulence ($\alpha_{\rm tu}$).} From the middle panels of Fig.~\ref{fig:param_comp}, we see that as expected, a flatter profile of the turbulent pressure directly translates into a flatter radio surface brightness profile. Since seed electrons are more concentrated toward the center (the collisional production of secondaries is more rapid there), and magnetic fields are stronger, concentrating the turbulence toward the cluster center for fixed $X_{\rm tu}$ results in higher radio luminosities, and slightly more curvature (due to the increased importance of cooling near the center). Overall, however, the spatial profile of turbulence has a much weaker effect than its overall normalization.

{\bf Impact of spatial profile of seed CRs $\alpha_{\rm CR, spat}$.} The spatial distribution of CRs has an even smaller impact on radio emission. At fixed total CR energy content $X_{\rm CR}$, concentrating the CRs towards the center leads to more centrally dominated surface brightness profiles, as expected, and higher radio luminosities (for the same reasons as above: secondaries are more easily produced in the center, and magnetic fields are stronger). We have also confirmed that radio surface brightness profiles scale linearly with $X_{\rm CR}$, as expected.

Overall, our results suggest that radio halos are much more sensitive to the level of turbulence (exponential dependence) rather than CR abundance (linear dependence), and that the spatial distribution of turbulence and CRs, while important, are second-order effects. In our parametrization, the most important controlling variable is $X_{\rm tu}$. The overall level of turbulence has to be such that $\tau_{\rm D} \sim \tau_{\rm cl}$ (see Table \ref{tab:timescales}), otherwise, too little or too much amplification takes place. For instance, for $X_\rmn{tu}\gtrsim0.08$, changing $X_\rmn{tu}$ by a factor of two changes the radio surface brightness by a factor of $\sim 10-100$ (see top panels of Fig.~\ref{fig:param_comp}). The required $\tau_{\rm D}/\tau_{\rm cl}$ depends only logarithmically on the abundance of seed CRs.

While the requirement of a threshold level of turbulence may explain why radio brightness is bimodal, it also raises a fine-tuning problem: why is the $L_{\rm radio}$ vs. $L_{\rm X}$ relation in active radio halos so tight? Depending on the details of infall or mergers, we would naturally expect fluctuations in $X_{\rm tu}$, which would translate into large scatter in the $L_{\rm radio}$--$L_{\rm X}$ relation. This can be only be understood if the timescale over which acceleration takes place $\tau_{\rm cl}$ also depends on the properties of turbulence, so that the the ratio $\tau_{\rm D}/\tau_{\rm cl}$ has relatively little scatter. We discuss one such scenario in \S\ref{sec:reacc}, but this point clearly deserves more work.

@@

The standard reacceleration model for radio halos requires two ingredients with
no current direct observational constraints: a CR population which produces seed
electrons, and turbulence to perform second-order Fermi acceleration on these
electrons\footnote{Other model ingredients, such as temperature, density, and
  B-field profiles, are observationally constrained by X-ray and Faraday
  rotation measurements.}. For the best studied radio halo, Coma, there are two
main observational constraints: the radio surface brightness profile
$S_{\nu}(r)$, and the integrated luminosity as a function of frequency
$L(\nu)$. For certain assumptions about turbulence and the seed population,
analytic theoretical models can match these observations \citep{brunetti11}, but
the realism of the assumed seed electron and turbulent profiles must be
confronted with numerical simulations.

Cluster turbulence has been studied numerically in cosmological simulations with
an eye toward radio halo properties \citep{2013ApJ...771..131B,
  miniati15}, though they were not confronted against the two
benchmark observations mentioned above. Most importantly, direct simulation of the
seed electron population has been missing in the literature. In this paper, we
fill that gap. At the same time, we study the sensitivity of radio halo profiles
and spectra to variation in properties of turbulence and seed population, and
uncover the dominant effects.
